### 2011-06-20 thesis/abstract.tex
Small fixes

In the context of mobile robotics, spatial concepts and semantics play a main role to perform
complex human-like tasks and human interactions. For handling those, a robot builds a representation
of space extended with semantic properties, process which is known as semantic mapping.
This representation identifies spatial entities and classifies them according to their meaning to
humans allowing the robot to reason at a very high-level, closer to humans.
For example, in a room scale level, humans categorize space in kitchens, bedrooms, corridors,
office, theater, etc\dots, by relating room areas with those categories describing expected
properties and actions that take place on them a robot can solve tasks like:
``Where are the cornflakes?''

>>>>

In the context of mobile robotics, spatial concepts and semantics play a main role to perform
complex human-like tasks and human interactions. For handling those, a robot builds a representation
of space extended with semantic properties, process which is known as semantic mapping.
This representation identifies spatial entities and classifies them according to their meaning to
humans allowing the robot to reason at a very high-level.
For example, in a room scale, humans categorize space in kitchens, bedrooms, corridors,
office, theater, computer lab, etc\dots, by relating room areas with those categories, that describing expected
properties and actions that take place on them, a robot can solve tasks like:
``Where are the cornflakes?''

### 2011-06-20 thesis/conclusion.tex
Small fixes

% Summary of developed work
This thesis studied the problem of detecting novel situations where a robot lacks knowledge to
correctly describe them.
It did so on the area of semantic mapping on indoor spaces, by detecting that none of known room
categories was able to correctly explain the sensed properties.

For that it reviewed novelty detection and how an optimal detector can be implemented by
thresholding. Showing after that, with the assumption of constant probability of seeing a
novel case, an optimal ordering function for thresholding can be implemented based on
the factor between a conditional and unconditional probability.

It studied the semantic mapping process proposed by \cite{pronobis2011semmap} and presented a method
to detect novel room categories based on probabilistic graphical models.
Using a synthetic dataset, respecting the assumptions, it showed that such a method would be optimal
if unconditional probability could be optimally approximated.
Since in realistic conditions unconditional probability cannot be implemented due to the lack of
knowing all the classes, some approaches were performed to approximate it with either a uniform
assumption or by approximating with simplified models using unlabelled data.

@@

After studying the used semantic mapping process and studying novelty detection methods, this
thesis proposed modelling a conditional and an unconditional probability distribution of sensed
data using graphical models. Under the presented assumptions and assuming both can be approximated
with perfect accuracy a ratio between those both probabilities would yield an optimal ordering
function for implementing a novelty detector.

@@

Additionally it was studied how the performance of the presented methods change as more data
is sensed from the environment. As expected all the methods increase their performance, but they
move further from what would optimally be expected.
Additionally the disadvantage between picking a uniform assumption and using an highly simplified
model for the unlabelled data, starts reducing as more information is available.
Nonetheless the model based on the usage of unlabelled data consistently lead to better detector
performance, being a strong indicator to use unlabelled data whenever there is access to it.

>>>>

% Summary of developed work
This thesis studied the problem of detecting novel situations where a robot lacks knowledge to
correctly describe them.
It did so on the area of semantic mapping on indoor spaces, by detecting that none of the known room
categories was able to correctly explain the sensed properties.

For that it reviewed novelty detection and how an optimal detector can be implemented by
thresholding. Showing after, that with the assumption of constant probability of seeing a
novel case an optimal ordering function for thresholding can be implemented based on
the factor between a conditional and unconditional probability.

It studied the semantic mapping process proposed by \cite{pronobis2011semmap} and presented a method
to detect novel room categories based on probabilistic graphical models.
Using a synthetic dataset, respecting the assumptions, it showed that such a method would be optimal
if unconditional probability could be optimally approximated.
Since, in realistic conditions, unconditional probability cannot be implemented due to the lack of
knowing all the classes, some approaches were performed to approximate it with either a uniform
assumption or by approximating with simplified models using unlabelled data.

@@

After studying the semantic mapping process and novelty detection methods, this
thesis proposed modelling the conditional and unconditional probability distribution of sensed
data using graphical models. Under the presented assumptions and assuming both can be exactly known
a ratio between those probabilities would yield an optimal ordering function for implementing a
novelty detector.

@@

Additionally it has studied how the performance of the presented methods change as more data
is sensed from the environment. As expected all the methods increase their performance, but they
move further away from what could be obtained with exact information.
Additionally the disadvantage between picking a uniform assumption and using an highly simplified
model for the unlabelled data, starts reducing as more information is available.
Nonetheless the model based on the usage of unlabelled data consistently lead to better detector
performance, being a strong indicator to use unlabelled data whenever there is access to it.
